### 2017-02-20 analysis-note-vf/results.tex
add subdirectory for the fermi motion study

\subsection{Incoherent beam-spin asymmetry}
Figure \ref{fig:bsa_incoh_bins} shows our measured incoherent beam-spin 
asymmetries, for the three sets of the two-dimensional bins as for the coherent 
channel. The $Q^2$, $x_{B}$, and $-t$-dependencies of $A_{LU}$ at 
$\phi$=~90$^{\circ}$ (the $\alpha$ parameter of the fit) are shown in figure 
\ref{fig:incoh_Q2_xB_t_ALU}.

>>>>

\subsection{Incoherent beam-spin asymmetry}
Figure \ref{fig:bsa_incoh_bins} shows our measured incoherent beam-spin 
asymmetries, for the three sets of the two-dimensional bins as for the 
incoherent channel. The $Q^2$, $x_{B}$, and $-t$-dependencies of $A_{LU}$ at 
$\phi$=~90$^{\circ}$ (the $\alpha$ parameter of the fit) are shown in figure 
\ref{fig:incoh_Q2_xB_t_ALU}.
